Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-12-09 paper/manuscript.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures/figX/Forward_Reverse_Fig.pdf}
    \caption{Free energy (in k$_{B}$T) for two different relative binding free energy (RBFE) perturbations. 
    Each plot shows the estimated free energy change using a varying fraction of total simulation time (up to 5 ns total). 
    The top panel shows the three-step protocol for a perturbation involving 5 perturbed atoms, while the bottom panel shows the same protocol for a perturbation involving 10 perturbed atoms. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}
    \label{fig:convergence_forward_reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures2/automatic-equilibration-detection/argon-potential.pdf}
    \includegraphics[width=0.95\linewidth]{paper/figures2/automatic-equilibration-detection/argon-potential-reverse-cumulative-average.pdf}
    \caption{{\bf Automatic partitioning into equilibration and production regions.}
    \emph{Top:} The average (black line) standard deviation (shaded region) of the reduced potential $u^*$ over many independent replicate simulations started from the same initial conditions show a significant initial transient before relaxing to the true average potential energy.
    \emph{Middle:} A cumulative average (red) of the entire simulation data demonstrates a bias in the estimate of the average potential $<u>$ that persists far beyond the initial transient relaxation time, while averaging a production region that omits the initial transient (blue) eliminates this bias.
    \emph{Bottom:} A simple automated approach to determination of the equilibration boundary $t_0$ suggested in \cite{chodera2016simple} examines the number of effectively uncorrelated samples $N_\mathrm{eff}_{[t_0,T]} = (T-t_0) / g_{[t_0,T]}$ within the proposed production region $[t_0,T]$ by computing the statistical inefficiency $g_{[t_0,T]}$ for that simulation interval.
    $N_\mathrm{eff}_{[t_0,T]}$ has the general behavior of increasing linearly as $t_0$ moves backwards from $T$ until the initial transient relaxation is encountered, at which point it plunges.
    The optimal equilibration boundary $t_0$ is selected to maximize the number of uncorrelated samples.
    \emph{Figure adapted from \cite{chodera2016simple}.}
    \todo[inline]{JDC will update this figure with something similar for a real alchemical free energy calculation.}
    }
    \label{fig:automatic-equilibration-detection}
\end{figure}

@@

\includegraphics[width=0.95\columnwidth]{paper/figures/fig8/Fig8.pdf}

@@

\todo[inline, color={green!20}]{ASJSM: Please upload the correct figure here and modify the path below}
\begin{figure}
    \includegraphics[width=0.95\linewidth]{fig6/free_energy_trajectories.pdf}
    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of ~5230 ns for OA-G3 and ~6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.
}
    \label{fig:freeenergytrajectories}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures/fig9_forward_reverse/Forward_Reverse_Fig.pdf}
    \caption{Free energy (in k$_{B}$T) for two different relative binding free energy (RBFE) perturbations. 
    Each plot shows the estimated free energy change using a varying fraction of total simulation time (up to 5 ns total). 
    The top panel shows the three-step protocol for a perturbation involving 5 perturbed atoms, while the bottom panel shows the same protocol for a perturbation involving 10 perturbed atoms. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}
    \label{fig:convergence_forward_reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures/fig10_equib_detection/fig10_equib.pdf}
    \caption{{\bf Automatic partitioning into equilibration and production regions.}
    \emph{Top:} The average (black line) standard deviation (shaded region) of the reduced potential $u^*$ over many independent replicate simulations started from the same initial conditions show a significant initial transient before relaxing to the true average potential energy.
    \emph{Middle:} A cumulative average (red) of the entire simulation data demonstrates a bias in the estimate of the average potential $<u>$ that persists far beyond the initial transient relaxation time, while averaging a production region that omits the initial transient (blue) eliminates this bias.
    \emph{Bottom:} A simple automated approach to determination of the equilibration boundary $t_0$ suggested in \cite{chodera2016simple} examines the number of effectively uncorrelated samples $N_\mathrm{eff}_{[t_0,T]} = (T-t_0) / g_{[t_0,T]}$ within the proposed production region $[t_0,T]$ by computing the statistical inefficiency $g_{[t_0,T]}$ for that simulation interval.
    $N_\mathrm{eff}_{[t_0,T]}$ has the general behavior of increasing linearly as $t_0$ moves backwards from $T$ until the initial transient relaxation is encountered, at which point it plunges.
    The optimal equilibration boundary $t_0$ is selected to maximize the number of uncorrelated samples.
    \emph{Figure adapted from \cite{chodera2016simple}.}
    \todo[inline]{JDC will update this figure with something similar for a real alchemical free energy calculation.}
    }
    \label{fig:automatic-equilibration-detection}
\end{figure}

@@

\includegraphics[width=0.95\columnwidth]{paper/figures/fig11_overlap/overlap_matrices.pdf}

@@

\todo[inline, color={green!20}]{ASJSM: Please upload the correct figure here and modify the path below}
\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig8_convergence/free_energy_trajectories.pdf}/free_energy_trajectories.pdf}
    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of ~5230 ns for OA-G3 and ~6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.
}
    \label{fig:freeenergytrajectories}
\end{figure}
